\documentclass[12pt]{article}
 
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{enumitem}

\newcommand{\problem}[1]{
	\vskip 1em
	{\large \textbf{#1}}
}
 
\begin{document}

\title{CS 1511 Homework 11} % Replace X with the appropriate number
\author{Mathew Varughese, Justin Kramer, Zach Smith} 
\date{Monday, Feb 25}

\maketitle


\setlength{\parskip}{.2em}
\setlength\parindent{0pt}
 
\problem{19. a}

EXACT INDSET = \{$<G, k> \mid $ the largest independent set in G has size exactly k\}.

To show EXACT INDSET $\in$ $\pi_2^p$, we need to demonstrate two things.

$\forall x \forall y \forall z$ T(x, y, z) runs in time $\mid x \mid^k$

$\forall x \exists y$ T(x, y, z) accepts iff x $\in$ EXACT INDSET

Our language will now become $\forall x$, with x being an independent set
of G, $\exists w$ where w is the largest independent set of size exactly k.

To solve this in poly-time, we will need 3 read-only tapes and 1 work tape, 
which is based on a simple scaling from our 2 read-only 1 work tape model
with $\pi_1^p$. 

Basically, it reads on the second tape the set of vertices. It goes through the tape 
and checks each vertex in the set and marks it on the graph (on the first tape). 
When it does this, 
it makes sure adjacent vertices are not touching to ensure it is an independent
set. 

Then, it checks the third tape, which is another set. It just needs to validate 
that this set is also a indepdent set and that it is larger or equal to in 
size to the set on the 2nd tape.

\problem{19. b}

SUCCINCT SET-COVER = \{$<S, n, k> $= : There is a subset of the collection of 3-DNF formulas S on n variables called S' where
S' evaluates to 1 for every assignment to its k variables\}.

To show SUCCINCT SET-COVER $\in$ $\Sigma_2^p$, we need to demonstrate two things.

$\forall x \forall y \forall z$ T(x, y, z) runs in time $\mid x \mid^k$

$\exists x \forall y$ T(x, y, z) accepts iff x $\in$ SUCCINCT SET-COVER

Our language will now become $\exists S'$, with S' being a subset of S, where
$\forall w$ combinations of k variable assignments, the formula evaluates to 1.

To solve this in poly-time, we will need 3 read-only tapes and 1 work tape, 
which is based on a simple scaling from our 2 read-only 1 work tape model
with $\Sigma_1^p$.

\problem{19. c}

VC-DIMENSION = \{$<C, k> $= : C represents a collection S s.t. VC(S) $\geq$ k\}.

To show VC-DIMENSION $\in$ $\Sigma_3^p$, we need to demonstrate two things.

$\forall x \forall y \forall z \forall  w$ T(x, y, z, w) runs in time $\mid x \mid^k$

$\exists x \forall y \exists z$ T(x, y, z, w) accepts iff x $\in$ VC-DIMENSION

Our language will now become $\exists C$, a Boolean circuit that $\forall X'$, where
X' a subset of the size of the largest set, $\exists i$ such that subset Si of S has an intersection
with X' that equals k and C(i, x) = 1.

To solve this in poly-time, we will need 4 read-only tapes and 1 work tape, 
which is based on a simple scaling from our 3 read-only 1 work tape model
with $\Sigma_2^p$.

\problem{20. a}

% 3SAT = \{$<\phi> $= : $\phi$ is a satisfiable 3CNF formula\}.

% To reduce 3SAT to its complement, we need to have an algorithm for 
% 3SAT that makes a call to its complement and runs in polynomial time.

% Here is the algorithm.

% L $\in$ 3SAT

% $\phi \in$ L iff $\phi \in $ the compliment of 3SAT

% Call to L($\phi$)

% $\phi_2= \neg \phi$

% Call to complement 3SAT($\phi_2$)

% This would mean that $\Sigma_n^p$ = $\pi_n^p$ with n = 1, and then
% for any n $\geq$ 1 we could define n TM's, with each having a one-to-one
% correspondence with their respective oracles of $\Sigma_n^p$. Then, we could
% say a TM M is a concatenation of M1  ... Mn to prove that $\Sigma_n^p$ answers yes
% iff M does so.

% If this would be possible in polynomial time, then we could take
% any element in NP, change it to its complement, run an algorithm 
% in co-NP with that element and show reducability in poly-time. 

% The same could be done with any element in co-NP, which would
% therefore make the languages equal.

% Also NP $\in \Sigma_1^p$ and co-NP $\in \pi_1^p$, so if the two sets of
% languages were equal then NP would equal co-NP by definition.

If 3SAT is reducible to its complement in Karp reductions then there 
exists a polynomial function $F$ such that  $x \in 3SAT \iff F(x) \in \overline{3SAT}$.

By this logic, since 3SAT is NP complete, every language L in NP can 
be reduced to 3SAT. And since this F exists, every language in NP 
could be reduced to $\overline{3SAT}$ in poly time. 

$\overline{3SAT} \in $ CoNP. So every language in NP would be in CoNP,
because then there would exists a reduction to $\overline{3SAT} $. This means
every L in NP would be in CoNP.

Also, if there is a reduction from 3SAT to its complement, then there exists 
a reduction from the complement of 3SAT to 3SAT. This is because if 
$A \leq B$, then $\overline{A} \leq \overline{B}$. This is because 
if there is a function to reduce a language to another in polynomial time, 
another function can be constructed for the complement of that language
which negates the membership. By this logic and the previous ideas, it can 
be shown every language in CoNP would be in NP. Therefore, CoNP = NP.


\problem{20. b}

With the same logic as the previous problem, the hierarchy would
eventually collapse so that any $\Sigma_n^p$ could equal any $\pi_n^p$ 
for the n=1 that the hierarchy collapses to. This would be a proof by induction
that repeats the previous problem for all complexity classes. In this complete collapse
to the bottom of the hierarchy, the union of all class PH would now be able to equal
NP.



\end{document}